\documentclass{resume}

%====================
% Personal Information
%====================
\name{Gordon Gouger}
\address{linkedin.com/in/gordon-gouger}
\address{ggouger.com}

\begin{document}

%====================
% Spacing tweaks for readability (not cramped)
%====================
\setlength{\itemsep}{-1pt}
\setlength{\parskip}{0.5pt}
\setlength{\parsep}{0pt}
\setlength{\topsep}{1pt}

%====================
% Experience
%====================
\begin{rSection}{Experience}
\vspace{1pt}

\begin{rSubsection}{Senior Machine Learning Engineer, Ozni AI}{September 2025 -- Present}{}{}
\begin{itemize}
\item Machine learning lead for two SBIR programs totaling \$4M in funding.
\item Responsible for intelligent sensing and Pattern of Life (PoL) analytics across vision, audio, and RF modalities.
\item Developed and deployed drone-based geolocation algorithms leveraging onboard sensing and edge AI inference.
\item Designed and implemented end-to-end ML systems spanning data ingestion, model training,
deployment, and field testing.
\item Deployed optimized models to constrained hardware including Raspberry Pi-class devices
using ONNX and TensorFlow Lite.
\item Owned full software and hardware architecture including sensor integration,
edge compute selection, and power constraints.
\item Built and maintained fully self-hosted CI/CD infrastructure using GitLab
for model training, validation, and deployment.
\item Curated and managed multi-terabyte datasets for signal detection,
classification, and model validation using real sensors and simulators.
\end{itemize}
\end{rSubsection}

\vspace{2pt}

\begin{rSubsection}{Principal AI Software Engineer, Northrop Grumman}{October 2021 -- September 2025}{}{}
\begin{itemize}
\item Machine learning technical lead on multiple rapid prototyping and
transition-to-production programs supporting operational systems.
\item Developed CNN-based modulation recognition models for narrowband and wideband RF,
including few-shot Siamese architectures.
\item Deployed optimized modulation recognition pipelines combining classical DSP features
(e.g., kurtosis) with CNN inference for IARPA programs.
\item Designed and trained transformer-based models for overhead imagery,
multi-spectral, hyperspectral, and wideband spectrum monitoring.
\item Built and deployed end-to-end emitter geolocation algorithms using Hawkeye 360 data,
including intercept-to-link-set generation.
\item Performed intelligence fusion across RF, vision, and metadata sources
for emitter classification and localization.
\item Deployed ML models to FPGA, NVIDIA Orin, and embedded edge platforms
using ONNX and TensorRT.
\item Created and curated multi-terabyte RF datasets using real radios
and high-fidelity simulators.
\item Built air-gapped systems utilizing locally hosted LLMs
for analysis, reasoning, and operator support.
\item Led and mentored multiple ML engineers; served as ML lead on programs
with cross-discipline teams.
\item Regularly interacted with customer leadership and supported deployment
into live operational environments.
\end{itemize}
\end{rSubsection}

\vspace{2pt}

\begin{rSubsection}{Engineer, Rincon Research Corporation}{June 2021 -- October 2021}{}{}
\begin{itemize}
\item Developed end to end GPS simulator.
\end{itemize}
\end{rSubsection}

\end{rSection}

%====================
% Education
%====================
\begin{rSection}{Education}
\vspace{1pt}
\item \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r r}
Master of Science in Electrical Engineering & May 2021 & GPA: 4.00 \\
Bachelor of Science in Engineering Physics & May 2020 & GPA: 3.96
\end{tabular*}

\end{rSubsection}
\end{rSection}

%====================
% Technical Strengths
%====================
\begin{rSection}{Technical Strengths}
\vspace{1pt}

FAA 107 Certified, Python, C++, C, MATLAB, Rust, CNNs, Transformers, Classical DSP + ML Hybrids,
Modulation Recognition, Geolocation, Sensor Fusion, ONNX, TensorRT,
TensorFlow Lite, Docker, Linux, GitLab CI/CD,
Azure, Agile, Jira, \LaTeX
\end{rSection}

%====================
% Clearance
%====================
\begin{rSection}{Clearance}
Active (but not currently held) TS/SCI
\end{rSection}

%====================
% Hobbies
%====================
\begin{rSection}{Hobbies \& Interests}
Running, Woodworking, Martial Arts, Glassblowing, Active in Local Church
\end{rSection}

\end{document}
